Further Evidence of Modified Spin-down in Sun-like Stars:\\Pile-ups in the Temperature--Period Distribution

### 2022-01-20 src/ms.tex
paper edits

We additionally fit the CKS long-period pile-up (using three different homogeneous \teff sources), the \citet{Hall2021} asteroseismic main-sequence sample, and all combined data sets of the long-period pile-up, allowing for \teff offsets in each data set (Table~\ref{tab:mcmc}). {\color{red} For the CKS pile-up stars and the \lamostmcq percentile curves, we assumed constant fractional \prot uncertainties of 10\%.} To isolate the long-period pile-up stars in the CKS sample, we selected a trapezoidal region using the condition $-0.0314~\teff + 199.286 < \prot < -0.0314~\teff + 206.286$. We note that this selection is particular to the CKS \teff scale and is not general. For the CKS sample, we additionally required $\logg~>~4$ and 5850~K~$<~\teff~<$~6500~K. In the joint fit of all data sets, the log likelihood was defined as the sum of log likelihoods (given by Eq.~\ref{eq:3}) from the individual data sets.

>>>>

We additionally fit the CKS long-period pile-up (using three different homogeneous \teff sources) and the \citet{Hall2021} asteroseismic main-sequence sample, allowing for \teff offsets in each data set (Table~\ref{tab:mcmc}). {\color{red} For the CKS pile-up stars and the \lamostmcq percentile curves, we assumed constant fractional \prot uncertainties of 10\%.} To isolate the long-period pile-up stars in the CKS sample, we selected a trapezoidal region using the condition $-0.0314~\teff + 199.286 < \prot < -0.0314~\teff + 206.286$. We note that this selection is particular to the CKS \teff scale and is not general. For the CKS sample, we additionally required $\logg~>~4$ and 5850~K~$<~\teff~<$~6500~K.

%, and all combined data sets of the long-period pile-up, 
% In the joint fit of all data sets, the log likelihood was defined as the sum of log likelihoods (given by Eq.~\ref{eq:3}) from the individual data sets.
